---
title: 'Problem Set #2'
author: "Cian Stryker"
date: "10/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(AER)
library(tidyverse)
library(fastDummies)
```

# Conceptual Questions


#### Question 1

\hfill\break

a.)

b.)

c.)

d.)

\hfill\break


#### Question 2

\hfill\break


#### Question 3

\hfill\break


#### Question 4

\hfill\break


#### Question 5

\hfill\break



#### Question 6

\hfill\break



#### Question 7

\hfill\break


#### Question 8

\hfill\break



#### Question 9

\hfill\break



\hfill\break


# Data Questions


```{r Setting up and Question 1}

data("Fatalities")

rows <- Fatalities %>%
  nrow()

rows_no_nas <- Fatalities %>%
  drop_na() %>%
  nrow()

data <- Fatalities %>%
  drop_na()

```

1.) One observation has missing values for at least one feature. 

```{r Question 2}

 q3 <- sapply(data, class)

```

2.) There are four categorical variables in the data set: state, breath, jail, and service. State has 50 different classes, but breath, jail, and service each only have two classes. 

```{r Question 3}

data2 <- data %>%
  dummy_cols(select_columns = c("breath", "jail", "service"), remove_selected_columns = TRUE, remove_first_dummy = TRUE)

model_1 <- lm(data = data2, fatal ~.)

summary_1 <- summary(model_1)

```

3.) The adjusted R^2 value is 0.999

```{r Question 4}

```

